Import_MCData

### 2024-03-06 Code/Import_MCData.Rmd
minor edit

This works because the OD680 & OD720 data are only episodically, but
widely, aberrant when a bubble interrupts the measurement, and if the
MultiCultivator is running properly these bubble aberration events are
rare.

>>>>

This works because the OD680 & OD720 data are only episodically, but
widely, aberrant when a bubble interrupts the measurement, and if the
Multicultivator is running properly these bubble aberration events are
rare.
